2019 Draft Prep

### 2019-03-23 draftPrep.Rmd
Hopefully the last core data changes before draft

# Data Set
```{r importFangraphs, include=FALSE}
fangraphs_pitchers <- "data/fangraphs_pitchers.Rds"
fangraphs_batters <- "data/fangraphs_batters.Rds"
pitchers_file <- "data/depthChartProjections_pitchers_20190321.csv"
batters_file <- "data/depthChartProjections_batters_20190321.csv"

@@

pitchers_draft %>%
  bind_rows(batters_draft) %>%
  mutate(round = ceiling(ADP/12)) %>%
  select(z_rank, Name, z_sum, round, ADP, positions) %>%
  arrange(z_rank) -> draft_df

>>>>

# Data Set
```{r importFangraphs, include=FALSE}
fangraphs_pitchers <- "data/fangraphs_pitchers.Rds"
fangraphs_batters <- "data/fangraphs_batters.Rds"
pitchers_file <- "data/depthChartProjections_pitchers_20190323.csv"
batters_file <- "data/depthChartProjections_batters_20190323.csv"

@@

pitchers_draft %>%
  bind_rows(batters_draft) %>%
  mutate(round = ceiling(ADP/12)) %>%
  arrange(z_sum %>% desc) %>%
  mutate(z_rank = row_number()) %>%
  select(z_rank, Name, z_sum, round, ADP, positions) -> draft_df
